Staged Abstract Interpreters

### 2019-09-08 paper/10_intro.tex
minor

Although the four artifacts may look dissimilar at first glance, they in
fact are all firmly rooted in the concrete semantics.  This
observation provides a way to abstract over the interpreter and achieve the
flexibility of reinterpreting the shared interpreter.  The generic interpreter
returns a value of monadic type, which can be varied by different semantics.
The value domains of the interpreter and the effects such as state and nondeterminism
can all be wrapped into this monadic type.  The binding-time abstraction is
represented by a higher-kinded type, and injected into the monadic type.  The
binding-times control whether the interpreter produces values directly or
generates code.

>>>>

Although the four artifacts may look dissimilar at first glance, they are in
fact all firmly rooted in the concrete semantics.  This observation provides a
way to abstract over the interpreter and achieve the flexibility of
reinterpreting the shared interpreter.  The generic interpreter returns a value
of monadic type, which vary based on semantics. The value domains
of the interpreter and the effects such as state and nondeterminism can all be
wrapped into this monadic type.  The binding-time abstraction is represented by
a higher-kinded type and injected into the monadic type.  The binding-times
control whether the interpreter produces values directly or generates code.
